ODE and Diffusion Models of Tumor Growth

### 2024-03-14 paper.tex
Moving to other machine

Hill then combined both equations to come to a conclusion on how lactic acid and oxygen would interact in a muscle.
The conclusions made from this section of the paper were essential for future models of diffusion. First, it was
assumed that the thickness $b > x'$ so none of the oxygen was able to penetrate through the entire system. From above, 
the concentrations of oxygen and lactic acid are $y$ and $y'$ respectively. Then the following graphic describes the system:

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{graphics/image.png}
    \caption{From 0 to 5 and 20 to 25, the concentration $y$ is equal to the steady state $y_0$. From 5 to 10,
    the concentration $y$ is decreasing until it reaches 0 at 10 (in green). From 10 to 15, the lactic acid concentration
    $y'$ (in blue) is increasing to its maximum and then decreases to 0 at 15. From 15 to 20, the oxygen concentration $y_0$ increases
    until reaching the steady state (red) at x = 20.}
    \label{fig:image}
\end{figure}

\end{document}

>>>>

Hill then combined both equations to come to a conclusion on how lactic acid and oxygen would interact in a muscle.

The conclusions made from this section of the paper were essential for future models of diffusion. First, it was
assumed that the thickness $b > x'$ so none of the oxygen was able to penetrate through the entire system. From above,
the concentrations of oxygen and lactic acid are $y$ and $y'$ respectively. Then the following graphic describes the system:

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{graphics/image.png}
    \caption{From 0 to 5 and 20 to 25, the concentration $y$ is equal to the steady state $y_0$. From 5 to 10,
    the concentration $y$ is decreasing until it reaches 0 at 10 (in green). From 10 to 15, the lactic acid concentration
    $y'$ (in blue) is increasing to its maximum and then decreases to 0 at 15. From 15 to 20, the oxygen concentration $y_0$ increases
    until reaching the steady state (red) at x = 20.}
    \label{fig:image}
\end{figure}

The diffusion equations that satisfy this model are the ones shown above. From the graphic, we can see that the oxygen concentration $y$ decreases from the steady state value $y_0$ at the boundary x = 0 until it reaches zero at x = 10. At the same time, the lactic acid concentration $y'$ increases from zero at x = 10, reaches a maximum, and then decreases back to zero at x = 15. Beyond x = 15, the oxygen concentration $y_0$ increases back to the steady state value at x = 20.
\end{document}
